\addcontentsline{toc}{chapter}{Daftar Pustaka}

\chapter*{DAFTAR PUSTAKA}

\noindent CQRS, data diperoleh melalui situs internet: https://martinfowler.com/bliki/CQRS.html. Diunduh pada tanggal 6 Juni 2025.

\noindent Vogels, W. (2009). Eventually Consistent. \emph{Communications of the ACM}, 40--44.

\noindent Kindsoon, Munoye., Martinek, Péter (2023): A Simplified Approach to Distributed Message Handling in a CQRS Architecture, \emph{Acta Polytechnica Hungarica.}

\noindent Armağan, Özgür., Gören-Sümer, Leyla (2014): Feedback control for multi-resource usage of virtualized database server, \emph{Computers and Electrical Engineering.}

\noindent Pan, Wenping., Mu, Dejun., Wu, Hangxing., Yao, Lei (2008): Feedback Control-based QoS Guarantees in Web Application Servers, \emph{IEEE International Conference on High Performance Computing and Communications.}

\noindent Das, T., Zhong, Y., Stoica, I., Shenker, S., dan Zaharia, M. (2018): Adaptive stream processing using dynamic batch sizing, \emph{Proceedings of the ACM Symposium on Cloud Computing.}

\noindent Gong, Siqian., Yin, Beibei., Cai, Kai-yuan (2018): An Adaptive PID Control for QoS Management in Cloud Computing System, \emph{IEEE International Symposium on Software Reliability Engineering Workshops.}

\noindent Wu, Han., Shang, Zhiao., Guang, Peng., Wolter, Katinka (2020). A Reactive Batching Strategy of Apache Kafka for Reliable Stream Processing in Real-time, \emph{IEEE International Symposium on Software Reliability Engineering.}

\noindent ZangLong (2017). Improvement and Implementation of a High Performance CQRS Architecture, \emph{International Conference on Robots \& Intelligent System..}

\noindent Bailis, Peter., Venkataraman, Shivaram., Franklin, Michael J., Hellerstein, Joseph M., Stoica, Ion (2017). Probabilistically Bounded Staleness for Practical Partial Quorums, \emph{International Conference on Robots \& Intelligent System.}

\noindent Kindsoon, Munoye., Martinek, Péter (2020). Evaluation of Data Storage Patterns in Microservices Archicture, \emph{IEEE 15th International Conference of System of Systems Engineering}

\noindent Ogata, K. (2010). \emph{Modern Control Engineering} (5th ed.). Prentice Hall. 793--798

\noindent Kleppmann, M. (2017). \emph{Designing Data-Intensive Applications: The Big Ideas Behind Reliable, Scalable, and Maintainable Systems}. O'Reilly Media. 389-391

\noindent Ljung, L. (1999): \emph{System identification: Theory for the user}, 2nd ed., Prentice Hall, Upper Saddle River

\noindent Newman, S. (2015). \emph{Building Microservices: Designing Fine-Grained Systems}. O'Reilly Media. 193--198

\noindent Brewer, E. (2000). Towards Robust Distributed Systems. \emph{Proceedings of the Annual ACM Symposium on Principles of Distributed Computing (PODC)}.
